Introducing Statistical Design of Experiments to SPARQL Endpoint Evaluation

### 2013-05-04 exp1/iswc2013.tex
A bit of tex-reorg
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@464 43ef1190-90fd-4dd7-a769-d0121f02b80e
describe factors in paper
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@496 43ef1190-90fd-4dd7-a769-d0121f02b80e

\documentclass{llncs}
%\documentclass{article}
\usepackage{cite}

\title{Introducing Statistical Design of Experiments to SPARQL
  Endpoint Evaluation}
\titlerunning{Introducing Design of Experiments to SPARQL Evaluation}
\author{Kjetil Kjernsmo\inst{1}}
\institute{Department of Informatics,
Postboks 1080 Blindern,
0316 Oslo, Norway
\email{kjekje@ifi.uio.no}}

@@

\maketitle

@@

The problematic sides of the benchmarking have been noted in several
papers, notably \cite{Duan:2011:AOC:1989323.1989340} and
\cite{conf/semweb/MontoyaVCRA12}. We also acknowledge that great
progress has been made to improve benchmarks, in particular, we are
indebted to \cite{mxro:Morsey2011DBpedia}.

@@

>>>>

%\documentclass{llncs}
\documentclass{article}
\usepackage{cite}
\usepackage{verbatim}

\title{Introducing Statistical Design of Experiments to SPARQL
  Endpoint Evaluation}
\author{Kjetil Kjernsmo\inst{1}}
%\titlerunning{Introducing Design of Experiments to SPARQL Evaluation}
%\institute{Department of Informatics,
%Postboks 1080 Blindern,
%0316 Oslo, Norway
%\email{kjekje@ifi.uio.no}}

%\maketitle

@@

@@

The problematic sides of the benchmarking have been noted in several
papers, notably \cite{Duan:2011:AOC:1989323.1989340} and
\cite{MontoyaVCRA12}. We also acknowledge that great
progress has been made to improve benchmarks, in particular, we are
indebted to \cite{mxro:Morsey2011DBpedia}.

@@

\section{Experimental setup}

As the focus of this paper is didactical, the actual measurements are
much simpler than what has been used in benchmarking.

To only deal with the relatively straightforward aspects of the DoE
formalism, we have chosen to constrain the experiment strictly to 2
levels. We have chosen 8 factors each having 2 levels, ``TripleC'' the number of triples in the
dataset, 1 or 2 MTriples, ``Machine'', which is the software and hardware platform,
where one machine runs GNU/Linux Debian Squeeze, has 16 GB RAM, an
Intel Core2 Duo E8500 CPU and two Parallell-ATA disks in a RAID-1
configuration. The other machine runs Debian Wheezy, has 8 GB RAM, an
Intel Core i7-3520M CPU and a single SSD on SATA-III.

Then, we test some language features: 
``BGPComp'', which is a Basic Graph Pattern of varying complexity. The
first level is:
\verbatiminput{experiment/BGPComp-1}
and the second level is 
\verbatiminput{experiment/BGPComp-1}

The following factors tests the absence (at level 1) or presence (at level 2) of the following clauses:
The ``Lang'' factor is this FILTER:
\verbatiminput{experiment/Lang-2}
and similarly,  ``Range'' is this FILTER:
\verbatiminput{experiment/Range-2}
``Union'' tests the following:
\verbatiminput{experiment/Union-2}
and ``Optional''
\verbatiminput{experiment/Optional-2}

Finally, ``Implement'' is the implementation undergoing
evaluation. Level 1 is running the new implementation, whereas Level 2
is the old implementation. The null hypothesis $H_0$ is that the old
implementation is as good as the new, and the alternative hypothesis
$H_1$ is that the new implementation has overall improved the
performance of the system.

We have used the dataset of \cite{mxro:Morsey2011DBpedia}, where
